Growth Dynamics of the Independent Gametophytes of *Pleurosoriopsis makinoi* (Polypodiaceae)

### 2019-05-06 ms.Rmd
Uncomment fig 5, load ggridges

```{r fig-5, evaluate = FALSE, fig.width=7, fig.height=8, fig.cap="Fig. 5. Density plots showing difference between microclimate at Pleurosoriopsis makinoi independent gametophyte site (Okutama) and sporophyte site (Uratakao). Significant differences (paired t-test) shown by asterisks: ***, p < 0.001; **, p < 0.01; * p < 0.05.  Y-axis is relative probability density; curves scaled so that total probability of each scales to 1. Vertical lines shown medians."}
# #' Extract p-values for plotting, and put into data frame
# #' with xvals specifying season and yvals specifying height 
# #' to plot asterisks.
# p_vals <-
#   t_test_results %>%
#   mutate(pval = case_when(
#     pval < 0.0001 ~ "***",
#     pval < 0.001 ~ "**",
#     pval < 0.05 ~ "*",
#     TRUE ~ ""
#   )) %>%
#   select(season, var, pval) %>%
#   spread(var, pval) %>%
#   rename(
#     par_total_pval = par_total,
#     rh_min_pval = rh_min,
#     temp_mean_pval = temp_mean
#   )
# 
# # Simple function to calculate maximum y-position for plotting asterisks.
# # Should be just above the mean + error bar height (1 sd).
# maxy <- function(x) {mean(x, na.rm = TRUE) + sd(x, na.rm = TRUE)}
# 
# pval_plot_data <- 
#   paired_microclimate %>%
#   select(-date, -month) %>%
#   group_by(season, site) %>%
#   summarize_all(
#     maxy
#   ) %>%
#   group_by(season) %>%
#   summarize_all(
#     max
#   ) %>%
#   select(-site) %>%
#   left_join(p_vals)
# 
# #' Format data for plotting: need columns to be mean and sd, by site and season.
# paired_means <- 
#   paired_microclimate %>%
#   select(-date) %>%
#   group_by(site, season) %>%
#   summarize_all(
#     list(~mean(., na.rm = TRUE),
#          ~sd(., na.rm = TRUE))
#   ) %>%
#   mutate(
#     season = factor(season, levels = c("winter", "spring", "summer", "fall"))
#   )
# 
# #' Make plot including t-test on three microclimatic variables.
# #' 
# #' The final plot includes multiple subplots. Each is a ridge plot showing 
# #' the distribution of one of the variables between the two sites, with the
# #' results of a paired t-test showing if they are different or not.
# #' 
# #' Need to manually set x ranges to keep x-axis scale the same across plots
# x_ranges <- tibble(var = selected_vars) %>%
#   mutate(
#     min = map_dbl(var, ~ pull(paired_microclimate, .) %>% min ),
#     max = map_dbl(var, ~ pull(paired_microclimate, .) %>% max )
#   )
# 
# # light blue / light green colorblind-friendly from colorbrewer
# # paired_colors <- c("#a6cee3", "#b2df8a")
# # OR dark blue / dark green colorblind-friendly from colorbrewer
# # paired_colors <- c("#1f78b4", "#33a02c")
# # OR dark grey / light grey for bw
# paired_colors <- c("grey55", "grey90")
# 
# subplots <- list()
# 
# #' Make ridge plots by mapping across nested datasets.
# plot_results <-
#   nested_paired_microclimate %>%
#   right_join(x_ranges) %>%
#   mutate(min = min - 0.05 * min,
#          max = max + 0.05 * max,
#          plot = pmap(list(var, data, x_min = min, x_max = max), 
#                      plot_ridges, 
#                      y_var = "site"),
#          pval = map2(var, data, run_t_test),
#          pval = case_when(
#            pval < 0.0001 ~ "***",
#            pval < 0.001 ~ "**",
#            pval < 0.05 ~ "*",
#            TRUE ~ ""
#          ),
#          plot = map2(
#            plot, pval, 
#            ~ .x + annotate("text", Inf, Inf, 
#                            label = .y, hjust = 1, vjust = 1))
#          
#          # If needed, add annotation for season to make sure subplots
#          # are positioned correctly
#          
#          # ,plot = map2(
#          #   plot, season,
#          #   ~ .x + annotate("text", -Inf, Inf,
#          #                   label = .y, hjust = -1, vjust = 1)),
#          # season = as_factor(season),
#          # season = fct_relevel(season, "winter", "spring", "summer", "fall")
#          
#   ) %>% 
#   arrange(season, var)
# 
# subplots <- plot_results$plot
# 
# #' Manually some subplots to remove redundant labels, etc.
# subplots[1:9] <- map(subplots[1:9], 
#                      ~ . + theme(axis.title.x = element_blank(),
#                                  axis.text.x = element_blank() ))
# 
# 
# subplots[1:12] <- map(subplots[1:12], 
#                       ~ . + scale_fill_manual(
#                         values = paired_colors,
#                         name="Site",
#                         breaks=c("okutama", "uratakao"),
#                         labels=c("Okutama", "Uratakao"))
# )
# 
# subplots[[10]] <- subplots[[10]] +
#   labs(x = expression(paste("DLI (", mol~m^-2~day^-1, ")", sep = "")) )
# 
# subplots[[11]] <- subplots[[11]] +
#   labs(x = expression("Min. Rel. Humidity (%)"))
# 
# subplots[[12]] <- subplots[[12]] +
#   labs(x = expression("Mean Temp. (°C)"))
# 
# #' Add titles.
# subplots <- map(subplots, ~ . + labs(title = "") )
# 
# subplots[[2]] <- subplots[[2]] +
#   labs(title = "Winter\n")
# 
# subplots[[5]] <- subplots[[5]] +
#   labs(title = "Spring\n")
# 
# subplots[[8]] <- subplots[[8]] +
#   labs(title = "Summer\n")
# 
# subplots[[11]] <- subplots[[11]] +
#   labs(title = "Fall\n")
# 
# #' Extract legend
# legend <- paired_microclimate %>%
#   ggplot(aes(x = temp_mean, y = site, fill = site)) +
#   geom_density_ridges() +
#   theme(legend.position = "bottom") +
#   scale_fill_manual(
#     values = paired_colors,
#     name="Site",
#     breaks=c("okutama", "uratakao"),
#     labels=c("Okutama", "Uratakao"))
# 
# legend <- get_legend(legend)
# 
# #' Combine and write out.
# subplots[[1]] +  subplots[[2]] +  subplots[[3]] + 
#   subplots[[4]] +  subplots[[5]] +  subplots[[6]] + 
#   subplots[[7]] +  subplots[[8]] +  subplots[[9]] + 
#   subplots[[10]] + subplots[[11]] + subplots[[12]] +
#   plot_spacer() + legend + plot_spacer() + plot_layout(ncol = 3, heights = c(1, 1, 1, 1, 0.2))

>>>>

```{r fig-5, evaluate = FALSE, fig.width=7, fig.height=8, fig.cap="Fig. 5. Density plots showing difference between microclimate at Pleurosoriopsis makinoi independent gametophyte site (Okutama) and sporophyte site (Uratakao). Significant differences (paired t-test) shown by asterisks: ***, p < 0.001; **, p < 0.01; * p < 0.05.  Y-axis is relative probability density; curves scaled so that total probability of each scales to 1. Vertical lines shown medians."}
#' Extract p-values for plotting, and put into data frame
#' with xvals specifying season and yvals specifying height
#' to plot asterisks.
p_vals <-
  t_test_results %>%
  mutate(pval = case_when(
    pval < 0.0001 ~ "***",
    pval < 0.001 ~ "**",
    pval < 0.05 ~ "*",
    TRUE ~ ""
  )) %>%
  select(season, var, pval) %>%
  spread(var, pval) %>%
  rename(
    par_total_pval = par_total,
    rh_min_pval = rh_min,
    temp_mean_pval = temp_mean
  )

# Simple function to calculate maximum y-position for plotting asterisks.
# Should be just above the mean + error bar height (1 sd).
maxy <- function(x) {mean(x, na.rm = TRUE) + sd(x, na.rm = TRUE)}

pval_plot_data <-
  paired_microclimate %>%
  select(-date, -month) %>%
  group_by(season, site) %>%
  summarize_all(
    maxy
  ) %>%
  group_by(season) %>%
  summarize_all(
    max
  ) %>%
  select(-site) %>%
  left_join(p_vals)

#' Format data for plotting: need columns to be mean and sd, by site and season.
paired_means <-
  paired_microclimate %>%
  select(-date) %>%
  group_by(site, season) %>%
  summarize_all(
    list(~mean(., na.rm = TRUE),
         ~sd(., na.rm = TRUE))
  ) %>%
  mutate(
    season = factor(season, levels = c("winter", "spring", "summer", "fall"))
  )

#' Make plot including t-test on three microclimatic variables.
#'
#' The final plot includes multiple subplots. Each is a ridge plot showing
#' the distribution of one of the variables between the two sites, with the
#' results of a paired t-test showing if they are different or not.
#'
#' Need to manually set x ranges to keep x-axis scale the same across plots
x_ranges <- tibble(var = selected_vars) %>%
  mutate(
    min = map_dbl(var, ~ pull(paired_microclimate, .) %>% min ),
    max = map_dbl(var, ~ pull(paired_microclimate, .) %>% max )
  )

# light blue / light green colorblind-friendly from colorbrewer
# paired_colors <- c("#a6cee3", "#b2df8a")
# OR dark blue / dark green colorblind-friendly from colorbrewer
# paired_colors <- c("#1f78b4", "#33a02c")
# OR dark grey / light grey for bw
paired_colors <- c("grey55", "grey90")

#' Make ridge plots by mapping across nested datasets.
plot_results <-
  nested_paired_microclimate %>%
  right_join(x_ranges) %>%
  mutate(min = min - 0.05 * min,
         max = max + 0.05 * max,
         plot = pmap(list(var, data, x_min = min, x_max = max),
                     plot_ridges,
                     y_var = "site"),
         pval = map2(var, data, run_t_test),
         pval = case_when(
           pval < 0.0001 ~ "***",
           pval < 0.001 ~ "**",
           pval < 0.05 ~ "*",
           TRUE ~ ""
         ),
         plot = map2(
           plot, pval,
           ~ .x + annotate("text", Inf, Inf,
                           label = .y, hjust = 1, vjust = 1))

         # If needed, add annotation for season to make sure subplots
         # are positioned correctly

         # ,plot = map2(
         #   plot, season,
         #   ~ .x + annotate("text", -Inf, Inf,
         #                   label = .y, hjust = -1, vjust = 1)),
         # season = as_factor(season),
         # season = fct_relevel(season, "winter", "spring", "summer", "fall")

  ) %>%
  arrange(season, var)

subplots <- plot_results$plot

#' Manually some subplots to remove redundant labels, etc.
subplots[1:9] <- map(subplots[1:9],
                     ~ . + theme(axis.title.x = element_blank(),
                                 axis.text.x = element_blank() ))

subplots[1:12] <- map(subplots[1:12],
                      ~ . + scale_fill_manual(
                        values = paired_colors,
                        name="Site",
                        breaks=c("okutama", "uratakao"),
                        labels=c("Okutama", "Uratakao"))
)

subplots[[10]] <- subplots[[10]] +
  labs(x = expression(paste("DLI (", mol~m^-2~day^-1, ")", sep = "")) )

subplots[[11]] <- subplots[[11]] +
  labs(x = expression("Min. Rel. Humidity (%)"))

subplots[[12]] <- subplots[[12]] +
  labs(x = expression("Mean Temp. (°C)"))

#' Add titles.
subplots <- map(subplots, ~ . + labs(title = "") )

subplots[[2]] <- subplots[[2]] +
  labs(title = "Winter\n")

subplots[[5]] <- subplots[[5]] +
  labs(title = "Spring\n")

subplots[[8]] <- subplots[[8]] +
  labs(title = "Summer\n")

subplots[[11]] <- subplots[[11]] +
  labs(title = "Fall\n")

#' Extract legend
legend <- paired_microclimate %>%
  ggplot(aes(x = temp_mean, y = site, fill = site)) +
  geom_density_ridges() +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    values = paired_colors,
    name="Site",
    breaks=c("okutama", "uratakao"),
    labels=c("Okutama", "Uratakao"))

legend <- get_legend(legend)

#' Combine and write out.
subplots[[1]] +  subplots[[2]] +  subplots[[3]] +
  subplots[[4]] +  subplots[[5]] +  subplots[[6]] +
  subplots[[7]] +  subplots[[8]] +  subplots[[9]] +
  subplots[[10]] + subplots[[11]] + subplots[[12]] +
  plot_spacer() + legend + plot_spacer() + plot_layout(ncol = 3, heights = c(1, 1, 1, 1, 0.2))
```
